\textsf{Are large language models superhuman chemists?}

### 2024-10-16 src/tex/ms.tex

\paragraph{Performance per topic} To obtain a more detailed understanding of the performance of the models, we also analyzed the performance of the models in different subfields of the chemical sciences.
For this analysis, we defined a set of topics (see \Cref{sec:meth-topic}). We classified all questions in the \chembench corpus into these topics based on hand-crafted rules and classifier models operating on the question texts.
We then computed the percentage of questions the models or humans answered correctly for each topic.
% \begin{figure}[!h]
%     \centering
%     \includegraphics{figures/all_questions_models_completely_correct_radar_human.pdf}
%     \caption{\textbf{Performance of the models and humans on the different topics of the \enquote{tiny} subset of the \chembench corpus.} The radar plot shows the performance of the models and humans on the different topics of \enquote{tiny} subset of the \chembench corpus. The performance is measured as the fraction of questions that were answered completely correctly by the models.
%     The best score for every dimension is one (all questions answered correctly), and the worst is zero (no question answered correctly). A larger colored area indicates a better performance.
%     This figure shows the performance on the subset of questions that were answered by humans. The performance of models on the entire corpus is shown in \Cref{fig:performance_per_topic}.
%     }
%     \label{fig:all_questions_models_completely_correct_radar_human}
%     \script{analyze_model_reports.py}
% \end{figure}

>>>>

\paragraph{Performance per topic} To obtain a more detailed understanding of the performance of the models, we also analyzed the performance of the models in different subfields of the chemical sciences.
For this analysis, we defined a set of topics (see \Cref{sec:meth-topic}). We classified all questions in the \chembench corpus into these topics based on hand-crafted rules and classifier models operating on the question texts.
We then computed the percentage of questions the models or humans answered correctly for each topic.
\begin{figure}[!h]
    \centering
    \includegraphics{figures/all_questions_models_completely_correct_radar_human.pdf}
    \caption{\textbf{Performance of the models and humans on the different topics of the \enquote{tiny} subset of the \chembench corpus.} The radar plot shows the performance of the models and humans on the different topics of \enquote{tiny} subset of the \chembench corpus. The performance is measured as the fraction of questions that were answered completely correctly by the models.
    The best score for every dimension is one (all questions answered correctly), and the worst is zero (no question answered correctly). A larger colored area indicates a better performance.
    This figure shows the performance on the subset of questions that were answered by humans. The performance of models on the entire corpus is shown in \Cref{fig:performance_per_topic}.
    }
    \label{fig:all_questions_models_completely_correct_radar_human}
    \script{analyze_model_reports.py}
\end{figure}
